Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsection{Experiment Method}
To perform experiment on the PRA system that has been created, the existing services in the Hipster Shop will be modified to imitate the behavior service that experiences performance regression. There are two main methods that can be used to create such behavior which are adding a sleep command and adding a loop with dereference operation of a variable which requires a lot of CPU power to solve it so that it is expected that the functions will have greater latency.
\section{Analysis}

>>>>

\subsection{Experiment Method}
To perform experiment on the PRA system that has been created, the existing services in the Hipster Shop will be modified to imitate the behavior service that experiences performance regression. There are two main methods that can be used to create such behavior which are adding a sleep command and adding a loop with dereference operation of a variable which requires a lot of CPU power to solve it so that it is expected that the functions will have more latency.

There are two stages that will be carried out to do this experiment, the first is baseline data collection stage. Baseline data will be taken by simulating
the usage of the application by using the Load Generator which will run with variable of \textbf{25 Users} and \textbf{5 Spawn Rates} for \textbf{1 hour}. This baseline data will then be stored by the engine for use in future test cases. The next step is to carry out experiment testing with cases which will be explained in more detail further.

\section{Analysis}
